### 2017-03-01 paper/chapters/gan.tex
removed irrelevant, misleading info
reformulation

\subsubsection{Feature Matching}
\label{ssub:gan_feature_matching}
In computer vision, features are often used to identify relevant pieces of information in images for recognition and classification.
They may refer to a set of points or edges in an image, which exactly is not clearly defined.
With the recent advances in classification tasks performed by deep convolutional networks, automatically learned features have been a large part of that success.
Feature matching is an technique designed to improve the learning procedure of GANs where not directly $\mathcal{L}_g$ is maximized but instead also learn the discriminator on intermediate layer activation outputs.
Using this modified procedure aids the generator to output data matching the statistics of the input data more closely.
%With $f(x)$ denoting an intermediate layer in $D$, the new objective function becomes:
%$$
%|| \mathbb{E}_{x \sim p_{data}}f(x) - \mathbb{E}_{z \sim p(z)}f(G(z)) || ^{2}_{2}
%$$

>>>>

\subsubsection{Feature Matching}
\label{ssub:gan_feature_matching}
In computer vision, features are often used to identify relevant pieces of information in images for recognition and classification.
With the recent advances in classification tasks performed by deep convolutional networks, automatically learned features have been a large part of that success.
Feature matching is an technique designed to improve the learning procedure of GANs where $\mathcal{L}_g$ is not not directly maximized but where the discriminator also learns on intermediate layer activation outputs.
Using this modified procedure aids the generator to output data matching the statistics of the input data more closely.
%With $f(x)$ denoting an intermediate layer in $D$, the new objective function becomes:
%$$
%|| \mathbb{E}_{x \sim p_{data}}f(x) - \mathbb{E}_{z \sim p(z)}f(G(z)) || ^{2}_{2}
%$$
